{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-08-01 documents/pulse_1.tex
Minted garbage

\documentclass[paper.tex]{subfiles}% ===> this file was generated automatically by noweave --- better not edit it
\begin{document}

@@

\nwfilename{pulse_1.nw}\nwbegindocs{1}\nwdocspar
Our aims with this experiment are to perform the following:

@@

<<pulse_1.py>>
import device_comms
import sweep

\nwenddocs{}\nwbegindocs{2}\nwdocspar

@@

# Phage+Bacteria / Bacteria-only / phage only?
# expose (parameters) / sham / thermal positives

@@

\end{document}
\nwenddocs{}

>>>>

\documentclass[paper.tex]{subfiles}
\begin{document}

@@

Our aims with this experiment are to perform the following:

@@

\begin{minted}[mathescape, fontsize=\small, xleftmargin=0.5em]{python}
import device_comms
import sweep
\end{minted}
\begin{minted}[fontsize=\small, xleftmargin=0.5em, mathescape, frame = leftline]{text}
---------------------------------------------------------------------------ModuleNotFoundError
Traceback (most recent call last)<ipython-input-1-821b060eb2e8> in
<module>
----> 1 import device_comms
      2 import sweep
ModuleNotFoundError: No module named 'device_comms'
\end{minted}

@@

# Phage+Bacteria / Bacteria-only / phage only?

# expose (parameters) / sham / thermal positives

@@

\end{document}
